PANNEURO_analysis

### 2020-09-15 PANNEURO_analysis.Rmd
variable creation script

@@

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
dim(dat.raw)
colnames(dat.raw)
```

```{r dat.coping summary, eval=FALSE, include=FALSE}
#summarytools::dfSummary(
#  dat.raw,
#  graph.col = F,
#  valid.col = F,
#  labels.col = F)
```

# Data availability

Data availability GAD
```{r gad availability}
dat.raw %>%
  freq(
    data_group_gad,
    cumul = F)
```

Data availability PHQ
```{r phq availability}
dat.raw %>%
  freq(
    data_group_phq,
    cumul = F)
```

Data availability PCL
```{r pcl availability}
dat.raw %>%
  freq(
    data_group_pcl,
    cumul = F)
```

Data availability OCI-R
```{r ocir availability}
dat.raw %>%
  freq(
    data_group_ocir,
    cumul = F)
```

```{r sample frequencies}
dat.raw %>%
  freq(Sample)
```

# COVID
## Recode variable
```{r covid test positive double}
dat.raw <- dat.raw %>%
  mutate(covid_test_positive_double_numeric =
           case_when(
             (respiratory.throat_swab_test_nose_numeric == 1 &
               respiratory.results_antibody_test_numeric == 1) ~ 2,
             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
             respiratory.results_antibody_test_numeric == 1 ~ 1,
             respiratory.results_antibody_test_numeric == 2 ~ 0
           )
         )

dat.raw <- dat.raw %>%
  mutate(covid_test_positive_double =
           recode_factor(
             covid_test_positive_double_numeric,
             `0` = "Negative",
             `1` = "Positive",
             `2` = "Double positive"
           )
         )

dat.raw %>%
  freq(covid_test_positive_double)
```

```{r gad covid test positive}
dat.raw <- dat.raw %>%
  mutate(gad.covid_test_positive_numeric =
           case_when(
             (respiratory.throat_swab_test_nose_numeric == 1 &
               respiratory.results_antibody_test_numeric == 1) ~ 1, # with two positive test results get coded as positive
             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
             respiratory.results_antibody_test_numeric == 1 ~ 1,
             respiratory.results_antibody_test_numeric == 2 ~ 0
           )
         )

dat.raw <- dat.raw %>%
  mutate(covid_test_positive =
           recode_factor(
             gad.covid_test_positive_numeric,
             `0` = "Negative",
             `1` = "Positive"
#             `2` = "Double positive"
           )
         )

dat.raw %>%
  freq(covid_test_positive)
```

>>>>

# ggplot theme
Set up ggplot theme for the plots
```{r ggplot theme}
theme_personal <-  theme(
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.y = element_blank(), 
    legend.background = element_blank(),
    legend.box.background = element_blank(),
    panel.background = element_blank(), 
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_line(
      colour = "gray",
      linetype = "dashed",
      size = 0.2
      ),
    axis.ticks = element_blank()
    )
```

@@

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds")) #NEEDS CHANGING
dim(dat.raw)
colnames(dat.raw)
```
